---
title: "p8105_hw1_al4225"
author: "Anjing"
date: "2022-09-19"
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Github:
https://github.com/al4225/p8105_hw1_Anjing.git


```{r penguins}
data("penguins", package = "palmerpenguins")
```

## Promlem 1
### The data in this dataset
In dataset **penguins**, it concludes the refined information of the study with 8 variables which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. 

The study name is PAL0708. The study is about 344 penguins from three species: Adelie, Gentoo and Chinstrap, and they are living in three islands: Biscoe, Dream and Torgersen. 

More details such as names and important values are as follows.

```{r data, echo = FALSE}
library(palmerpenguins)
head(penguins)
summary(penguins)
```

### The size of the dataset
There are 344 rows and 8 total columns in **penguins**.
```{r size}
nrow(penguins)
ncol(penguins)
```

### The mean flipper length
The mean of flipper length is 200.9152.
```{r mean}

mean(penguins$flipper_length_mm, na.rm = TRUE)
```

### Plot
We can also visualize the Penguins by making a scatterplot of flipper_length_mm (y) vs bill_length_mm (x). Each color represents a different species.

```{r plot, warning = FALSE}
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave(file = "penguins.jpg" )
```

## Problem 2

This is a practice to better use these data types. 

### Create a data frame

1) a random sample of size 10 from a standard Normal distribution.
2) a logical vector indicating whether elements of the sample are greater than 0.
3) a character vector of length 10. I choose "NO1", "NO2", "NO3", "NO4", "NO5", "NO6", "NO7", "NO8", "NO9", "NO10" as character vectors.
4) a factor vector of length 10, with 3 different factor “levels”, I choose "NY", "NJ", "MA" as three different levels.

```{r probmen2, warning = FALSE}
library(tidyverse)
problem2_df = tibble(
  x = rnorm(10),
  vec_char = c("NO1", "NO2", "NO3", "NO4", "NO5", "NO6", "NO7", "NO8", "NO9", "NO10" ),
  vec_logical = c(x >= 0),
  vec_factor = factor(c("NY", "NJ", "MA", "NY", "NJ", "MA","NY", "NJ", "MA", "NY"), levels = c("NY", "NJ", "MA"))
)
problem2_df
```

### Take the mean of each variable in my dataframe. 
We can see that the x and vec_logical variables work and the others don't work.

```{r, warning = FALSE}
problem2_df %>%
  pull(x) %>%
  mean()

problem2_df %>%
  pull(vec_char) %>%
  mean()

problem2_df %>%
  pull(vec_logical) %>%
  mean()

problem2_df %>%
  pull(vec_factor) %>%
  mean()
```

### Convert variables.
I apply the function of **as.numeric** to the logical, character, and factor variables. After that, their classes become numeric. We can explain the last problem about the mean. This is because we cannot calculate the mean of character and factor. We can only calculate the mean of numbers.
```{r}
factor = factor(c(1, 2, 3))
print(factor)
class(factor)
factor.1 = as.numeric(factor)
print(factor.1)
class(factor.1)

character = ("1" )
print(character)
class(character)
character.1 = as.numeric(character)
print(character.1)
class(character.1)

x = c(1, -1)
logical = (c(x >= 0))
print(logical)
class(logical)
logical.1 = as.numeric(logical)
print(logical.1)
class(logical.1)
```

