---
title: "p8105_hw1_al4225"
author: "Anjing"
date: "2022-09-19"
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Github:
https://github.com/al4225/p8105_hw1_Anjing.git


```{r penguins}
data("penguins", package = "palmerpenguins")
```

## Promlem 1
### the data in this dataset
In dataset **penguins**, it concludes the refined information of the study with 8 variables which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. 

The study name is PAL0708. The study is about 344 penguins from three species: Adelie, Gentoo and Chinstrap, and they are living in three islands: Biscoe, Dream and Torgersen. 

More details such as names and important values are as follows.

```{r data, echo = FALSE}
library(palmerpenguins)
head(penguins)
summary(penguins)
```
### the size of the dataset

There are 344 rows and 8 total columns in **penguins**.
```{r size}
nrow(penguins)
ncol(penguins)
```


### the mean flipper length
The mean of flipper length is 200.9152.

```{r mean}

mean(penguins$flipper_length_mm, na.rm = TRUE)
```

### Plot
We can also visualize the Penguins by making a scatterplot of flipper_length_mm (y) vs bill_length_mm (x). Each color represents a different species.

```{r plot, warning = FALSE}
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave(file = "penguins.jpg" )
```
